---
title: "Unit Test Practice"
format: html
editor: visual
---

## unit testing with the `testthat` package

First install packages
```{r}
library(testthat)
library(devtools)
library(remotes)
```

Write a function to practice unit tests.

This function is going to find the mean value of each column, and then return the
lowest and highest mean value calculated (in that order)

we would expext
- the output to be numeric
- output shoult be a vector of lenth 2
- first value should be smaller than the second value

```{r}
mean_range <- function( df) {
   #return the mean values of each column
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE) 
 #find min and max values
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  #return min and max values in that order
  return(c(col_mean_min, col_mean_max))
}

mean_range( df = mtcars)
```

Write some unit tests!
```{r}
#| include: false
#test that the output us length of length 2
expect_length(mean_range(df = mtcars), 2)
```








